GSE74548: Gene Methylation Enrichment Analysis

### 2022-05-12 gmea.Rmd
fixed a bug with promoter analysis

# DM3 - post trial supplement versus placebo

@@

# testing
dm <- head(dm,40000)

@@

dm <- read.table("dma3a.tsv.gz")
dm <- subset(dm,Regulatory_Feature_Group == "Promoter_Associated")

# testing
dm <- head(dm,20000)

@@

#download.file("https://reactome.org/download/current/ReactomePathways.gmt.zip", destfile="ReactomePathways.gmt.zip")
#unzip("ReactomePathways.gmt.zip")
genesets <- gmt_import("ReactomePathways.gmt")

@@

#download.file("https://reactome.org/download/current/ReactomePathways.gmt.zip", destfile="ReactomePathw>
#unzip("ReactomePathways.gmt.zip")
genesets <- gmt_import("ReactomePathways.gmt")

@@

mitch_report(mmres,outfile="mitch_multi.html",overwrite=TRUE)

>>>>

# DM3 - association of Hcy with gene methylation

It is thought that high plasma homocysteine can inhibit DNA methylation.
Let's see whether that is the case, and which genes are most affected.
This analysis is conducted at the whole gene level as well as on the level of promoters.

@@

# testing
#dm <- head(dm,40000)

@@

dm <- read.table("dma3a.tsv.gz")
dm <- dm[grep("Promoter_Associated",dm$Regulatory_Feature_Group),]

# testing
#dm <- head(dm,20000)

@@

genesets <- gmt_import("ReactomePathways.gmt")

@@

genesets <- gmt_import("ReactomePathways.gmt")

@@

#mitch_report(mmres,outfile="mitch_multi.html",overwrite=TRUE)
